---
title: "Class 11 Section 3 Onward"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include=FALSE}
#knitr::knit_hooks$set(webgl = hook_webgl)
knitr::knit_hooks$set(rgl = function(before, options, envir) {
  if (!before) {
    ## after a chunk has been evaluated
    if (rgl.cur() == 0) return()  # no active device
    name = paste(options$fig.path, options$label, sep = '')
    rgl.snapshot(paste(name, '.png', sep = ''), fmt = 'png')
    return(paste('\\includegraphics{', name, '}\n', sep = ''))
  }
})
```

## Bio3D Class 11

If you don't have the [bio3d package](http://thegrantlab.org/bio3d/) available then you will need to do a one-time-only install from within R like so:

```{r, eval=FALSE}
install.packages("bio3d")
```


Now we are sure we have the package lets load it and read some PDB files for analysis. Note in the code-block below we can add the option `warning=FALSE` to turn off the printing of the warning msg about files already existing.

```{r, warning=FALSE, results='hide'}
library(bio3d)

# Download some example PDB files 
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)
```

Lets align these structures with the `pdbaln()` function and print a summary of the output.

```{r}
# Extract and align the chains we are interested in  
pdbs <- pdbaln(files, fit = TRUE)
pdbs
```

I wonder how this call will work

```{r}
aln2html(pdbs)
```

Can we see the results [alignment.html](alignment.html)


### Sequence analysis

Lets try some basic things...

```{r}
# Calculate sequence 
identity <- seqidentity(pdbs)
identity
```

and RMSD



```{r}
# Calculate RMSD  
rd <- rmsd(pdbs)   
```

Lets add some names to our RMSD matrix for convenience

```{r}
rownames(rd) <- basename.pdb(pdbs$id)
colnames(rd) <- basename.pdb(pdbs$id)
rd
```

And cluster into 2 or 3 grps?

```{r}
# Clustering  
hc <- hclust(as.dist(rd))  
grps <- cutree(hc, k=3) 
```

and a plot...

```{r}
# Plot results as dendrogram  
hclustplot(hc, k=3)
```



and try a fancy heatmap

```{r}
library(pheatmap)
pheatmap(rd)
```

Play with colors and add a little gap for our first clear grp

```{r}
co <- colorRampPalette( c("white", "firebrick3"))
pheatmap(rd, color = co(15), cutree_row = 2, cutree_col = 2)
```

and some sequence conservation analysis

```{r, fig.cap="High value bars represent conserved positions/residues"}
x <- conserv(pdbs)
plot(x, typ="h", xlab="Alignment Position", ylab="Conservation")
```

## PCA example

Now for some PCA of these structures

```{r}
pc <- pca(pdbs, rm.gaps=TRUE)
plot(pc, col=grps)
```

And a 3D plot

```{r fancy-rgl, rgl=TRUE, warning=FALSE}
library(rgl)

plot3d(pc$z[,1], pc$z[,2], pc$z[,3], col=grps, type="s")
```

## Stop for the day here 

Report in session setup.
```{r}
sessionInfo()
```

